Next Trippy Structures\thanks{Supported by organization x.}

### 2018-12-21 paper.tex
Minor ref fixes

\usepackage{enumerate}
\usepackage[linesnumbered,commentsnumbered,boxed]{algorithm2e}
\usepackage{marginnote}

@@

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}
We took the idea from our SPIRE paper and we made it great, using ZSTD compression and other tricks to improve the time complexity of the queries for the TTCTR. Regarding AccumM, it was not possible to improve its speed (as it was already a few memory accesses per query), but we managed to compress it without increasing time complexity. We rock.

\section{State of the Art}
A nice review of all the R-Tree derivatives: \cite{john2017performance}.

@@

Cite Adrian and all that crap.

Cite ways of obtaining the data we need, to show that it's possible even though we couldn't get any. You can get a lot of info from smart cards \cite{bhaskar2015passenger}, smart cards + gps \cite{ma2014development}, and even cellphone data \cite{liu2017exploring}. These guys also focus on trajectory reconstruction \cite{tao2014exploring}. These guys \cite{wang2014aggregated} made it so boring that they are probably not worth citing. To the ones who wonder how do we know the final stops, they figured it out in \cite{alsger2016validating}.

>>>>

\usepackage{enumerate}
\usepackage{marginnote}
\usepackage[linesnumbered,commentsnumbered,boxed]{algorithm2e}

@@

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}
We took the idea from our SPIRE paper and we made it great, using ZSTD compression and other tricks to improve the time complexity of the queries for the \ctr. Regarding \acumm, it was not possible to improve its speed (as it was already a few memory accesses per query), but we managed to compress it without increasing time complexity. We rock.

\section{Related works}
A nice review of all the R-Tree derivatives: \cite{john2017performance}.

@@

Cite Adrian and all that crap. Also send an email to Andrea asking about \cite{rivera2018faster}; I couldn't read it yet as it's paywalled and not available on sci-hub yet!\marginnote{Contact Andrea and Diego!}

Cite ways of obtaining the data we need, to show that it's possible even though we couldn't get any. You can get a lot of info from smart cards \cite{bhaskar2015passenger}, smart cards + gps \cite{ma2014development}, and even cellphone data \cite{liu2017exploring}. These guys also focus on trajectory reconstruction \cite{tao2014exploring}. These guys \cite{wang2014aggregated} made it so boring that they are probably not worth citing, but I'm keeping them here for now because they separate fridays and types of days, even though we don't care much about that anymore. OR DO WE? To the ones who wonder how do we know the final stops, they figured it out in \cite{alsger2016validating}. Basically what we need is called \textbf{trip-chaining}.
